KidsAIR: merge health datasets

### 2020-06-30 merge_datasets.Rmd
exposure analysis updates

exposure_analysis_data_medium <- exposure_analysis_data_long_new %>% 
  select(area, home, home_winter_id, winter_id, treatment_assigned, treatment_actual, 
         sampling_day, sample_date, burn_level:mean_temp_roll_4day) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, winter_id, treatment_assigned, treatment_actual, 
         sampling_day, child_id_char, burn_level:mean_temp_roll_4day) %>% 
  mutate(filter_var = if_else(winter_id == 1 & is.na(sampling_day) & lead(sampling_day) == 1, 1, 0),
         filter_var = if_else(is.na(filter_var), 0, filter_var)) %>% 
  select(filter_var, area:mean_temp_roll_4day) %>% 
  filter(filter_var == 0) %>% 
  select(-filter_var) %>% 
  ungroup()

@@

exposure_analysis_data_medium <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_medium.rds"))
exposure_analysis_data_long <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_long_new.rds")) 
sums_rolling_pm_data <- 
  read_rds(paste0(file_path, "Output/sums_rolling_pm_data.rds"))

exposure_analysis_data_short <- exposure_analysis_data_medium %>% 
  arrange(area, home, winter_id) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  # Sum home activity vars over entire sampling period to make 1 obs per sampling period
  mutate(home_act_gas = factor(home_act_gas, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_gas = as.character(home_act_gas),
         home_act_gas = as.numeric(home_act_gas),
         home_act_gas_sum = sum(home_act_gas),
         home_act_elect = factor(home_act_elect, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_elect = as.character(home_act_elect),
         home_act_elect = as.numeric(home_act_elect),
         home_act_elect_sum = sum(home_act_elect),
         home_act_propane = factor(home_act_propane, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_propane = as.character(home_act_propane),
         home_act_propane = as.numeric(home_act_propane),
         home_act_propane_sum = sum(home_act_propane),
         home_act_oil = factor(home_act_oil, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_oil = as.character(home_act_oil),
         home_act_oil = as.numeric(home_act_oil),
         home_act_oil_sum = sum(home_act_oil),
         home_act_other = factor(home_act_other, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_other = as.character(home_act_other),
         home_act_other = as.numeric(home_act_other),
         home_act_other_sum = sum(home_act_other),
         home_act_smoking = factor(home_act_smoking, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_smoking = as.character(home_act_smoking),
         home_act_smoking = as.numeric(home_act_smoking),
         home_act_smoking_sum = sum(home_act_smoking),
         home_act_incense = factor(home_act_incense, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_incense = as.character(home_act_incense),
         home_act_incense = as.numeric(home_act_incense),
         home_act_incense_sum = sum(home_act_incense),
         home_act_candle = factor(home_act_candle, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_candle = as.character(home_act_candle),
         home_act_candle = as.numeric(home_act_candle),
         home_act_candle_sum = sum(home_act_candle),
         home_act_kerosene = factor(home_act_kerosene, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_kerosene = as.character(home_act_kerosene),
         home_act_kerosene = as.numeric(home_act_kerosene),
         home_act_kerosene_sum = sum(home_act_kerosene),
         home_act_windows = factor(home_act_windows, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_windows = as.character(home_act_windows),
         home_act_windows = as.numeric(home_act_windows),
         home_act_windows_sum = sum(home_act_windows),
         home_act_door = factor(home_act_door, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_door = as.character(home_act_door),
         home_act_door = as.numeric(home_act_door),
         home_act_door_sum = sum(home_act_door),
         home_act_sweep = factor(home_act_sweep, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_sweep = as.character(home_act_sweep),
         home_act_sweep = as.numeric(home_act_sweep),
         home_act_sweep_sum = sum(home_act_sweep)) %>% 
  group_by(area, home, winter_id) %>% 
  distinct(child_id_char, .keep_all = TRUE) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  arrange(area, home, winter_id)

>>>>

exposure_analysis_data_long <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_long_new.rds")) 
sums_rolling_pm_data <- 
  read_rds(paste0(file_path, "Output/sums_rolling_pm_data.rds"))

exposure_analysis_data_medium <- exposure_analysis_data_long %>% 
  select(area, home, home_winter_id, winter_id, treatment_assigned, treatment_actual, 
         sampling_day, sample_date, burn_level:mean_temp_roll_4day) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, winter_id, treatment_assigned, treatment_actual, 
         sampling_day, child_id_char, burn_level:mean_temp_roll_4day) %>% 
  mutate(filter_var = if_else(winter_id == 1 & is.na(sampling_day) & lead(sampling_day) == 1, 1, 0),
         filter_var = if_else(is.na(filter_var), 0, filter_var)) %>% 
  select(filter_var, area:mean_temp_roll_4day) %>% 
  filter(filter_var == 0) %>% 
  select(-filter_var) %>% 
  arrange(area, home, winter_id) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  # Sum home activity vars over entire sampling period to make 1 obs per sampling period
  mutate(home_act_gas = factor(home_act_gas, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_gas = as.character(home_act_gas),
         home_act_gas = as.numeric(home_act_gas),
         home_act_gas_sum = sum(home_act_gas),
         home_act_elect = factor(home_act_elect, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_elect = as.character(home_act_elect),
         home_act_elect = as.numeric(home_act_elect),
         home_act_elect_sum = sum(home_act_elect),
         home_act_propane = factor(home_act_propane, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_propane = as.character(home_act_propane),
         home_act_propane = as.numeric(home_act_propane),
         home_act_propane_sum = sum(home_act_propane),
         home_act_oil = factor(home_act_oil, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_oil = as.character(home_act_oil),
         home_act_oil = as.numeric(home_act_oil),
         home_act_oil_sum = sum(home_act_oil),
         home_act_other = factor(home_act_other, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_other = as.character(home_act_other),
         home_act_other = as.numeric(home_act_other),
         home_act_other_sum = sum(home_act_other),
         home_act_smoking = factor(home_act_smoking, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_smoking = as.character(home_act_smoking),
         home_act_smoking = as.numeric(home_act_smoking),
         home_act_smoking_sum = sum(home_act_smoking),
         home_act_incense = factor(home_act_incense, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_incense = as.character(home_act_incense),
         home_act_incense = as.numeric(home_act_incense),
         home_act_incense_sum = sum(home_act_incense),
         home_act_candle = factor(home_act_candle, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_candle = as.character(home_act_candle),
         home_act_candle = as.numeric(home_act_candle),
         home_act_candle_sum = sum(home_act_candle),
         home_act_kerosene = factor(home_act_kerosene, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_kerosene = as.character(home_act_kerosene),
         home_act_kerosene = as.numeric(home_act_kerosene),
         home_act_kerosene_sum = sum(home_act_kerosene),
         home_act_windows = factor(home_act_windows, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_windows = as.character(home_act_windows),
         home_act_windows = as.numeric(home_act_windows),
         home_act_windows_sum = sum(home_act_windows),
         home_act_door = factor(home_act_door, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_door = as.character(home_act_door),
         home_act_door = as.numeric(home_act_door),
         home_act_door_sum = sum(home_act_door),
         home_act_sweep = factor(home_act_sweep, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_sweep = as.character(home_act_sweep),
         home_act_sweep = as.numeric(home_act_sweep),
         home_act_sweep_sum = sum(home_act_sweep)) %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home"))

@@

exposure_analysis_data_medium <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_medium.rds"))

exposure_analysis_data_short <- exposure_analysis_data_medium %>% 
  group_by(area, home, winter_id) %>% 
  distinct(child_id_char, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

### 2020-06-30 merge_health_datasets.Rmd
exposure analysis updates

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  full_join(exposure_analysis_data_medium,
            by = c("area", "child_id_num", "home", "home_winter_id", "winter_id", 
                   "treatment_assigned", "treatment_actual",
                   "sampling_day")) %>% 
  filter(!is.na(home))

>>>>

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) %>% 
  select(child_id_num, child_id_char, area, winter_id)

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  full_join(exposure_analysis_data_medium,
            by = c("area", "child_id_num", "home", "home_winter_id", "winter_id", 
                   "treatment_assigned", "treatment_actual",
                   "sampling_day")) %>% 
  filter(!is.na(home)) %>% 
  filter(!is.na(child_id_num)) %>% 
  select(-child_id_char) %>% 
  left_join(demographics, by = c("area", "winter_id", "child_id_num")) %>% 
  select(area:child_id_num, child_id_char, visit_date:amb_pm_sampling_period_5)
